\section{Experience}
% \subsection{Vocational}
%
\cventry{Dec 2022\\Mar 2023}{C++/Qt Counselor Senior Developer}{Perticon}{Remote - Tehran}{}{
  \begin{itemize}%
    \item As part of the development team, develop an image processing app for fruit sorters.
    \item Participation in the construction of the derailment hardware.
    \item Used pytorch and cuda to identification of healthy fruit.
    \item Implemented CI/CD to build project on the github actions.
  \end{itemize}%
}
%
\cventry{Aug 2022\\Dec 2022}{C++/Qt Counselor and Developer}{Pardiotech}{Remote - Tehran}{}{
  \begin{itemize}%
    \item Resolved Qt-related problems and fixed bugs in existing Identification of bone density software.
    \item The bone range identification and editing section has been implemented.
    \item In the radiography picture, I implemented custom polygons to mark bones.
  \end{itemize}%
}
%
\cventry{Jul 2020\\Aug 2022}{Senior C++/Qt Developer}{Hype1}{Remote - Sydney}{}{
  \begin{itemize}%
    \item Lead the development team to develop a software to asphalt damage identification.
    \item Worked with an image processing team and developed a software to identify asphalt damage and defects.
    \item Developed a new modules to use in the project, like qmldock and qml table view.
    \item Implemented qml dock library for using in project (QDockWidgets implementation in qml).
    \item Implemented CI/CD to build project on the github actions.
  \end{itemize}%
}
%
\cventry{Oct 2015\\Jul 2020}{Senior Software engineer}{Tooska LTD}{Astara}{}{
  \begin{itemize}%
    \item Lead the development team to develop application and websites for customers including app and websites.
    \item Developed quiz game for Android with Qt/qml.
    \item Developed a home media app for trains running on raspberry pi.
    \item Commercial and e-commerce web sites.
  \end{itemize}%
}
%
\cventry{Jun 2012\\Oct 2015}{Senior C++/Qt developer}{Tooska LTD}{Astara}{}{
  \begin{itemize}%
     \item Developed voip softphone for windows, linux and mac using pjsip and Qt framework.
     \item Used rest api to getting user balance \& profile informations.
  \end{itemize}%
}
%
\cventry{Aug 2010\\Jun 2012}{Software engineer}{Tooj LTD}{Astara}{}{
  \begin{itemize}%
    \item Working on some app \& website projects.
    \item Developed some Qt applications.
  \end{itemize}%
}
%
\cventry{Feb 2006\\May 2010}{C\# Windows application developer}{Dade kavan}{Astara}{}{
  \begin{itemize}%
    \item Developed accounting and enterprise applications using .NET Framework.
    \item Worked on government accounting softwares like: Municipal accounting system.
  \end{itemize}%
}
%
% \cventry{Aug 2010-Oct 2014}{Software engineer}{Tooj LTD}{Astara}{}{
%   \begin{itemize}
%     \item Lead development team.
%     \item Working on some app & website projects
%     \item Developing some Qt applications.
%   \end{itemize}%
% }
%
% \cventry{Feb 2006-May 2010}{C# Windows application developer}{Dade kavan}{Astara}{}{
%   \begin{itemize}
%     \item Developed accounting and enterprise applications using .NET Framework.
%     \item Worked on government accounting softwares like: Municipal accounting system.
%   \end{itemize}%
% }


% \begin{itemize}
% \item Achievement 1
% \item Achievement 2 (with sub-achievements)
%   \begin{itemize}
%   \item Sub-achievement (a);
%   \item Sub-achievement (b), with sub-sub-achievements (don't do this!);
%     \begin{itemize}
%     \item Sub-sub-achievement i;
%     \item Sub-sub-achievement ii;
%     \item Sub-sub-achievement iii;
%     \end{itemize}
%   \item Sub-achievement (c);
%   \end{itemize}
% \item Achievement 3
% \item Achievement 4
% \end{itemize}}
% \cventry{year--year}{Job title}{Employer}{City}{}{Description line 1Description line 2Description line 3}
% \subsection{Miscellaneous}
% \cventry{year--year}{Job title}{Employer}{City}{}{Description}

